---
title: "Quick Maps for Prospect Development"
author: "Tarak Shah"
date: "`r Sys.Date()`"
output: html_document
---
```{r,  echo=FALSE}
library(knitr)
opts_chunk$set(cache=TRUE, cache.path = 'DocumentName_cache/', fig.path='figure/')
```

`pdquickmap` is a small tool to make it easier to visualize geographic data. 
If you start out with a data set that includes addresses, `pdquickmap` has 
functions that can append geocodes to the data and create a map in the 
javascript library leaflet.js. These maps can be saved as HTML files and sent to clients. 

To get started, you'll need to have `devtools` installed in order to install 
packages from GitHub, and you'll need to instal a few other packages:

```{r install_packages, eval=FALSE}
install.packages(c("devtools", "RgoogleMaps"))
devtools::install_github('ramnathv/rCharts')
devtools::install_github('tarakc02/pdquickmap')
```

And finally, you'll need to load the `pdquickmap` library:
```{r loadlib}
library(pdquickmap)
```

Now you're ready to go! Let's start with a sample data frame that's included, called `urel`:
```{r urel}
data(urel)
urel
```

This is a pretty common setup, whether the data has come from a report or `webi` or what have you. Importantly, notice that we have address information, but no geocodes for our data. The address fields are `street`, `city`, `state`, and `zip`. In order to map these addresses, we'll need to add geocodes using `append_geocode`. In addition to the entire data frame, we need to let the function know which of the fields are the address fields. We do this by listing the names of the fields:

```{r geocode}
cols = c("street", "city", "state", "zip")
geo_data <- append_geocode(urel, cols)
geo_data
```

Now we're ready to map, and for that we just need to run `make_leaflet`: 

```{r make_leaflet, eval=FALSE}
make_leaflet(geo_data)
```

```{r show_leaflet, echo=FALSE, comment=NA, results='asis', tidy=FALSE, message=FALSE}
L <- make_leaflet(geo_data)
L$show('iframesrc', standalone = TRUE)
```

Note the way that `make_leaflet` automatically added the data from the data frame into the popups on the map, so that whe you click on a dot you see the name, address, and so on (the "latitude" and "longitude" columns are automatically excluded). You may not want every single column of your data frame to be part of the popups on the map, though, and you can control this behavior by selecting the columns from your data that should be in the pop-up, using `popup_columns`: 

```{r make_leaflet2, eval=FALSE}
make_leaflet(geo_data, popup_columns = c("names", "giving"))
```
```{r show_leaflet2, echo=FALSE, comment=NA, results='asis', tidy=FALSE}
L2 <- make_leaflet(geo_data, popup_columns = c("names", "giving"))
L2$show('iframesrc', standalone=TRUE)
```